Untitled

### 2022-06-13 paper_comparison/explore/check_different_sigma.Rmd
upload check model

>>>>

# New design

Sigma: 2

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

Sigma: 5

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 5)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

Sigma: 10

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 10)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

Sigma: 2

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

Sigma: 5

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 5)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

Sigma: 10

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 10)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

Sigma: 2

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

Sigma: 5

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 5)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

Sigma: 10

```{r fig.height=18, fig.width=24, cache = TRUE}
mod <- simple_cubic_model(x = rand_uniform(-1, 1), sigma = 10)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

### 2022-06-13 paper_comparison/explore/check_poly_model.Rmd
explore poly model
upload check model

Sigma: 0.125

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.125)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

Sigma: 0.25

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.25)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

Sigma: 0.125

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.125)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(100, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

Sigma: 0.25

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.25)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(100, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(100, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(100, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

Sigma: 0.125

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.125)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(300, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

Sigma: 0.25

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 0.25)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(300, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

for (a in c(2, 3, 4, 5, 6)) {

  i <- i + 1
  mod$set_prm("a", a) %>%
    {.$gen(300, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("a:{a}")) -> plot_list[[i]]

@@

>>>>

@@

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

@@

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

Sigma: 2

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

Sigma: 4

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 4)
ori_dat <- mod$gen(50)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

@@

@@

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

@@

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

Sigma: 2

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

Sigma: 4

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 4)
ori_dat <- mod$gen(100)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

@@

@@

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

@@

Sigma: 2

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 2)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]

Sigma: 4

```{r fig.height=6, fig.width=8, cache = TRUE}
mod <- poly_model(2, x = rand_uniform(-1, 1), sigma = 4)
ori_dat <- mod$gen(300)
i <- 0
plot_list <- list()

for (shape in c(1, 2, 3, 4)) {

  i <- i + 1
  mod$set_prm("shape", shape) %>%
    {.$gen(50, computed = select(ori_dat, x, e))} %>%
    {mod$plot(., remove_axis = TRUE, remove_grid_line = TRUE, theme = theme_light())} +
    ggtitle(glue::glue("shape:{shape}")) -> plot_list[[i]]
